### 2022-11-15 dissertation/chapters/08-results.tex
🚧 (results): WIP replotting tables

% Table generated by Excel2LaTeX from sheet 'results - test - loss'
\begin{table}[H]

@@

		\begin{tabular}{rlccc|c|c|c|c|c|ccccc}
			epoch                                                                          & 30                 &                                                                                &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
			                                                                               &                    &                                                                                &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
			                                                                               &                    & \multicolumn{1}{l}{\textbf{heuristic}}                                         &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
			\cmidrule{3-3}\cmidrule{6-6}\cmidrule{8-8}\cmidrule{10-10}    \textbf{dataset} & \textbf{statistic} & \textbf{adagrad}                                                               & \textbf{adam}                                                                  & \textbf{nag}                                                                   & \textbf{bhh\_gd}                                & \textbf{rmsprop}                                                               & \textbf{bhh\_all}                               & \textbf{adadelta}                                                              & \textbf{bhh\_mh}                                & \textbf{ga}                                     & \textbf{sgd}                                    & \textbf{pso}                                    & \textbf{momentum}                               & \textbf{de}                                     \\

@@

			abalone                                                                        & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
			                                                                               & avg                & \cellcolor[rgb]{ .506,  .776,  .486}1.967785                                   & \cellcolor[rgb]{ .494,  .773,  .486}1.965134827                                & \cellcolor[rgb]{ .765,  .851,  .502}2.0156043                                  & \cellcolor[rgb]{ .749,  .847,  .502}2.012517173 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{1.94553315}  & \cellcolor[rgb]{ 1,  .922,  .518}2.058704583    & \cellcolor[rgb]{ .788,  .859,  .502}2.019921077                                & \cellcolor[rgb]{ .996,  .827,  .502}2.29420573  & \cellcolor[rgb]{ .984,  .612,  .459}2.81545685  & \cellcolor[rgb]{ .992,  .773,  .49}2.42804241   & \cellcolor[rgb]{ .98,  .522,  .443}3.038417873  & \cellcolor[rgb]{ .992,  .745,  .486}2.494169393 & \cellcolor[rgb]{ .973,  .412,  .42}3.295858177  \\
			                                                                               & std                & 0.031577789                                                                    & 0.034949967                                                                    & 0.034657443                                                                    & 0.068121366                                     & 0.035183664                                                                    & 0.087594488                                     & 0.034405331                                                                    & 0.055085207                                     & 0.055148148                                     & 0.028810924                                     & 0.293755503                                     & 0.029086341                                     & 0.016489872                                     \\
			adult                                                                          & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
			                                                                               & avg                & \cellcolor[rgb]{ 1,  .922,  .518}0.346737798                                   & \cellcolor[rgb]{ 1,  .922,  .518}0.38233353                                    & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.313320884} & \cellcolor[rgb]{ .788,  .859,  .502}0.335180995 & \cellcolor[rgb]{ .933,  .902,  .514}0.343292783                                & \cellcolor[rgb]{ .973,  .412,  .42}586.2065996  & \cellcolor[rgb]{ .467,  .765,  .486}0.317677033                                & \cellcolor[rgb]{ 1,  .922,  .518}0.363543899    & \cellcolor[rgb]{ 1,  .922,  .518}0.392047161    & \cellcolor[rgb]{ .388,  .745,  .482}0.313329677 & \cellcolor[rgb]{ 1,  .922,  .518}1.217724345    & \cellcolor[rgb]{ .388,  .745,  .482}0.313444396 & \cellcolor[rgb]{ 1,  .922,  .518}0.639695856    \\
			                                                                               & std                & 0.003704238                                                                    & 0.018067239                                                                    & 0.000510377                                                                    & 0.043628962                                     & 0.014659665                                                                    & 1261.204704                                     & 0.005277776                                                                    & 0.020803371                                     & 0.020086997                                     & 0.000411017                                     & 0.496591684                                     & 0.0003947                                       & 0.042558869                                     \\
			air quality                                                                    & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
			                                                                               & avg                & \cellcolor[rgb]{ .651,  .82,  .494}0.256871193                                 & \cellcolor[rgb]{ .827,  .871,  .506}0.260623969                                & \cellcolor[rgb]{ .647,  .82,  .494}0.256829053                                 & \cellcolor[rgb]{ 1,  .922,  .518}0.264177871    & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.251334045} & \cellcolor[rgb]{ .996,  .827,  .502}0.272859303 & \cellcolor[rgb]{ .647,  .82,  .494}0.256781683                                 & \cellcolor[rgb]{ .976,  .914,  .514}0.263703859 & \cellcolor[rgb]{ .996,  .792,  .494}0.275862527 & \cellcolor[rgb]{ .988,  .69,  .475}0.285172782  & \cellcolor[rgb]{ .984,  .608,  .459}0.292264593 & \cellcolor[rgb]{ .984,  .604,  .459}0.292851261 & \cellcolor[rgb]{ .973,  .412,  .42}0.309698115  \\
			                                                                               & std                & 0.007475522                                                                    & 0.008912099                                                                    & 0.005955119                                                                    & 0.011452365                                     & 0.007814891                                                                    & 0.016310047                                     & 0.00630808                                                                     & 0.007306605                                     & 0.008162884                                     & 0.014769128                                     & 0.022648597                                     & 0.016417541                                     & 0.017044223                                     \\
			bank                                                                           & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\

>>>>

\begin{sidewaystable}[htbp]
		\begin{tabular}{r|ccc|c|c|c|c|c|ccccc}
			                              & \multicolumn{13}{c}{\textbf{BHH vs. Low-Level Heuristics - Average Rank}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \\
			\textbf{dataset}              & \textbf{adagrad}                                                          & \textbf{adam}                                           & \textbf{rmsprop}                                        & \textbf{bhh\_gd}                                        & \textbf{nag}                                            & \textbf{bhh\_all}                                       & \textbf{adadelta}                                       & \textbf{bhh\_mh}                                        & \textbf{ga}                                              & \textbf{pso}                                             & \textbf{sgd}                                             & \textbf{momentum}                                        & \textbf{de}                                              \\
			\textbf{abalone}              & \cellcolor[rgb]{ .388,  .745,  .482}2.2215 ($\pm$1.591)                   & \cellcolor[rgb]{ .416,  .753,  .482}2.3989 ($\pm$1.887) & \cellcolor[rgb]{ .78,  .859,  .502}4.6172 ($\pm$2.65)   & \cellcolor[rgb]{ .796,  .863,  .506}4.7032 ($\pm$2.108) & \cellcolor[rgb]{ .725,  .839,  .498}4.2731 ($\pm$1.542) & \cellcolor[rgb]{ 1,  .922,  .518}5.9376 ($\pm$2.399)    & \cellcolor[rgb]{ .894,  .89,  .51}5.3129 ($\pm$1.478)   & \cellcolor[rgb]{ .992,  .749,  .486}8.1882 ($\pm$1.195) & \cellcolor[rgb]{ .98,  .525,  .443}11.1108 ($\pm$1.102)  & \cellcolor[rgb]{ .98,  .514,  .439}11.2559 ($\pm$1.826)  & \cellcolor[rgb]{ .992,  .718,  .478}8.628 ($\pm$1.019)   & \cellcolor[rgb]{ .984,  .624,  .463}9.8151 ($\pm$1.16)   & \cellcolor[rgb]{ .973,  .412,  .42}12.5376 ($\pm$1.329)  \\
			\textbf{air\_quality}         & \cellcolor[rgb]{ .427,  .757,  .482}3.6409 ($\pm$2.259)                   & \cellcolor[rgb]{ .804,  .863,  .506}5.4312 ($\pm$2.62)  & \cellcolor[rgb]{ .388,  .745,  .482}3.4452 ($\pm$2.57)  & \cellcolor[rgb]{ .729,  .843,  .502}5.0817 ($\pm$2.762) & \cellcolor[rgb]{ .467,  .765,  .486}3.8194 ($\pm$2.229) & \cellcolor[rgb]{ 1,  .894,  .514}6.686 ($\pm$3.061)     & \cellcolor[rgb]{ .765,  .851,  .502}5.2441 ($\pm$3.162) & \cellcolor[rgb]{ 1,  .922,  .518}6.357 ($\pm$2.303)     & \cellcolor[rgb]{ .996,  .784,  .494}7.8204 ($\pm$2.265)  & \cellcolor[rgb]{ .984,  .588,  .455}9.9151 ($\pm$2.288)  & \cellcolor[rgb]{ .98,  .518,  .443}10.6613 ($\pm$1.606)  & \cellcolor[rgb]{ .973,  .412,  .42}11.7559 ($\pm$1.473)  & \cellcolor[rgb]{ .976,  .471,  .431}11.1419 ($\pm$2.236) \\
			\textbf{bank}                 & \cellcolor[rgb]{ .455,  .765,  .486}2.5495 ($\pm$1.598)                   & \cellcolor[rgb]{ .388,  .745,  .482}2.0796 ($\pm$1.587) & \cellcolor[rgb]{ .588,  .8,  .49}3.4645 ($\pm$2.209)    & \cellcolor[rgb]{ .8,  .863,  .506}4.8828 ($\pm$1.702)   & \cellcolor[rgb]{ .71,  .835,  .498}4.2871 ($\pm$1.732)  & \cellcolor[rgb]{ 1,  .922,  .518}6.2419 ($\pm$2.157)    & \cellcolor[rgb]{ .914,  .894,  .51}5.672 ($\pm$1.241)   & \cellcolor[rgb]{ .988,  .639,  .463}9.7495 ($\pm$1.048) & \cellcolor[rgb]{ .98,  .537,  .447}10.9817 ($\pm$1.216)  & \cellcolor[rgb]{ .976,  .467,  .431}11.8376 ($\pm$1.464) & \cellcolor[rgb]{ .992,  .757,  .486}8.2774 ($\pm$1.03)   & \cellcolor[rgb]{ .992,  .741,  .486}8.4774 ($\pm$1.068)  & \cellcolor[rgb]{ .973,  .412,  .42}12.4989 ($\pm$1.224)  \\
			\textbf{bike}                 & \cellcolor[rgb]{ .388,  .745,  .482}1.7204 ($\pm$1.384)                   & \cellcolor[rgb]{ .643,  .816,  .494}3.6925 ($\pm$4.004) & \cellcolor[rgb]{ .973,  .914,  .514}6.2624 ($\pm$4.58)  & \cellcolor[rgb]{ .663,  .824,  .498}3.8441 ($\pm$1.398) & \cellcolor[rgb]{ 1,  .922,  .518}6.4516 ($\pm$1.02)     & \cellcolor[rgb]{ .71,  .835,  .498}4.2151 ($\pm$1.361)  & \cellcolor[rgb]{ .859,  .878,  .506}5.3602 ($\pm$1.155) & \cellcolor[rgb]{ .996,  .843,  .506}7.4108 ($\pm$1.008) & \cellcolor[rgb]{ .988,  .686,  .475}9.2269 ($\pm$1.183)  & \cellcolor[rgb]{ .988,  .682,  .475}9.3086 ($\pm$1.761)  & \cellcolor[rgb]{ .984,  .596,  .455}10.3355 ($\pm$1.419) & \cellcolor[rgb]{ .984,  .561,  .451}10.7086 ($\pm$1.423) & \cellcolor[rgb]{ .973,  .412,  .42}12.4634 ($\pm$1.465)  \\
			\textbf{car}                  & \cellcolor[rgb]{ .702,  .835,  .498}4.7634 ($\pm$0.938)                   & \cellcolor[rgb]{ .388,  .745,  .482}1.6226 ($\pm$1.405) & \cellcolor[rgb]{ .455,  .765,  .486}2.3269 ($\pm$1.409) & \cellcolor[rgb]{ .561,  .792,  .49}3.3473 ($\pm$1.35)   & \cellcolor[rgb]{ .831,  .871,  .506}6.0785 ($\pm$0.799) & \cellcolor[rgb]{ .58,  .8,  .49}3.5624 ($\pm$1.315)     & \cellcolor[rgb]{ 1,  .922,  .518}7.7344 ($\pm$1.746)    & \cellcolor[rgb]{ .996,  .8,  .498}8.8505 ($\pm$1.413)   & \cellcolor[rgb]{ .984,  .592,  .455}10.7763 ($\pm$1.471) & \cellcolor[rgb]{ 1,  .855,  .506}8.3613 ($\pm$1.622)     & \cellcolor[rgb]{ .988,  .651,  .467}10.2452 ($\pm$1.447) & \cellcolor[rgb]{ .984,  .576,  .451}10.9226 ($\pm$1.349) & \cellcolor[rgb]{ .973,  .412,  .42}12.4086 ($\pm$1.492)  \\
			\textbf{diabetic}             & \cellcolor[rgb]{ .506,  .776,  .486}2.7796 ($\pm$1.659)                   & \cellcolor[rgb]{ 1,  .886,  .514}7.1484 ($\pm$2.227)    & \cellcolor[rgb]{ 1,  .922,  .518}6.7376 ($\pm$2.577)    & \cellcolor[rgb]{ .812,  .867,  .506}5.2269 ($\pm$2.186) & \cellcolor[rgb]{ .388,  .745,  .482}1.8118 ($\pm$1.413) & \cellcolor[rgb]{ .988,  .69,  .475}9.3968 ($\pm$3.022)  & \cellcolor[rgb]{ .494,  .773,  .486}2.6753 ($\pm$1.629) & \cellcolor[rgb]{ .992,  .765,  .49}8.557 ($\pm$1.17)    & \cellcolor[rgb]{ .98,  .529,  .443}11.2011 ($\pm$1.413)  & \cellcolor[rgb]{ .984,  .573,  .451}10.7022 ($\pm$1.067) & \cellcolor[rgb]{ .898,  .89,  .51}5.9215 ($\pm$1.542)    & \cellcolor[rgb]{ .949,  .906,  .514}6.3355 ($\pm$1.612)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5065 ($\pm$1.242)  \\
			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .533,  .784,  .49}4.2645 ($\pm$2.614)                    & \cellcolor[rgb]{ .388,  .745,  .482}3.6022 ($\pm$2.445) & \cellcolor[rgb]{ .388,  .745,  .482}3.5946 ($\pm$2.329) & \cellcolor[rgb]{ .784,  .859,  .502}5.4118 ($\pm$2.665) & \cellcolor[rgb]{ .89,  .89,  .51}5.8914 ($\pm$2.629)    & \cellcolor[rgb]{ .875,  .886,  .51}5.829 ($\pm$2.856)   & \cellcolor[rgb]{ .996,  .788,  .494}7.914 ($\pm$3.429)  & \cellcolor[rgb]{ 1,  .922,  .518}6.3849 ($\pm$2.944)    & \cellcolor[rgb]{ 1,  .894,  .514}6.7043 ($\pm$2.82)      & \cellcolor[rgb]{ .996,  .82,  .498}7.5731 ($\pm$2.982)   & \cellcolor[rgb]{ .976,  .471,  .431}11.5785 ($\pm$1.459) & \cellcolor[rgb]{ .973,  .412,  .42}12.2301 ($\pm$1.382)  & \cellcolor[rgb]{ .984,  .608,  .459}10.0215 ($\pm$2.358) \\
			\textbf{forest\_fires}        & \cellcolor[rgb]{ .769,  .855,  .502}5.1559 ($\pm$2.922)                   & \cellcolor[rgb]{ .388,  .745,  .482}4.2688 ($\pm$2.984) & \cellcolor[rgb]{ .718,  .839,  .498}5.0355 ($\pm$3.143) & \cellcolor[rgb]{ .569,  .796,  .49}4.6935 ($\pm$2.759)  & \cellcolor[rgb]{ 1,  .922,  .518}5.6882 ($\pm$2.215)    & \cellcolor[rgb]{ .91,  .894,  .51}5.4839 ($\pm$3.107)   & \cellcolor[rgb]{ 1,  .859,  .506}6.5161 ($\pm$3.082)    & \cellcolor[rgb]{ .898,  .89,  .51}5.4591 ($\pm$2.668)   & \cellcolor[rgb]{ .996,  .796,  .494}7.3667 ($\pm$2.37)   & \cellcolor[rgb]{ 1,  .863,  .51}6.4796 ($\pm$3.354)      & \cellcolor[rgb]{ .98,  .529,  .443}10.8129 ($\pm$1.207)  & \cellcolor[rgb]{ .976,  .463,  .431}11.7065 ($\pm$1.325) & \cellcolor[rgb]{ .973,  .412,  .42}12.3333 ($\pm$1.923)  \\
			\textbf{housing}              & \cellcolor[rgb]{ .404,  .749,  .482}3.4484 ($\pm$2.025)                   & \cellcolor[rgb]{ .388,  .745,  .482}3.3344 ($\pm$1.819) & \cellcolor[rgb]{ .439,  .757,  .482}3.6946 ($\pm$2.166) & \cellcolor[rgb]{ .553,  .792,  .49}4.4742 ($\pm$2.312)  & \cellcolor[rgb]{ .584,  .8,  .49}4.6839 ($\pm$2.658)    & \cellcolor[rgb]{ .537,  .788,  .49}4.3763 ($\pm$2.438)  & \cellcolor[rgb]{ 1,  .918,  .518}7.5903 ($\pm$2.748)    & \cellcolor[rgb]{ 1,  .922,  .518}7.5441 ($\pm$1.736)    & \cellcolor[rgb]{ 1,  .878,  .51}7.8839 ($\pm$2.099)      & \cellcolor[rgb]{ .984,  .608,  .459}9.9409 ($\pm$2.317)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4075 ($\pm$1.528)  & \cellcolor[rgb]{ .976,  .431,  .424}11.2731 ($\pm$1.506) & \cellcolor[rgb]{ .976,  .42,  .424}11.3484 ($\pm$2.096)  \\
			\textbf{iris}                 & \cellcolor[rgb]{ .965,  .91,  .514}6.3946 ($\pm$1.6)                      & \cellcolor[rgb]{ .525,  .784,  .49}3.5839 ($\pm$2.511)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6968 ($\pm$1.912) & \cellcolor[rgb]{ .706,  .835,  .498}4.7473 ($\pm$2.275) & \cellcolor[rgb]{ .522,  .78,  .486}3.5548 ($\pm$2.125)  & \cellcolor[rgb]{ .78,  .859,  .502}5.2204 ($\pm$3.041)  & \cellcolor[rgb]{ .973,  .412,  .42}11.3527 ($\pm$1.779) & \cellcolor[rgb]{ 1,  .922,  .518}6.6075 ($\pm$2.555)    & \cellcolor[rgb]{ .992,  .749,  .486}8.2473 ($\pm$1.765)  & \cellcolor[rgb]{ .992,  .745,  .486}8.2731 ($\pm$4.384)  & \cellcolor[rgb]{ .98,  .518,  .443}10.3796 ($\pm$1.294)  & \cellcolor[rgb]{ .976,  .447,  .427}11.0548 ($\pm$1.409) & \cellcolor[rgb]{ .988,  .678,  .471}8.8871 ($\pm$3.251)  \\
			\textbf{mushroom}             & \cellcolor[rgb]{ .71,  .835,  .498}4.4656 ($\pm$1.053)                    & \cellcolor[rgb]{ .388,  .745,  .482}2.1344 ($\pm$1.883) & \cellcolor[rgb]{ .431,  .757,  .482}2.4656 ($\pm$1.359) & \cellcolor[rgb]{ .569,  .796,  .49}3.4484 ($\pm$1.602)  & \cellcolor[rgb]{ .969,  .91,  .514}6.3323 ($\pm$0.891)  & \cellcolor[rgb]{ .6,  .804,  .494}3.6688 ($\pm$2.469)   & \cellcolor[rgb]{ 1,  .922,  .518}6.5538 ($\pm$1.071)    & \cellcolor[rgb]{ .992,  .718,  .478}9.0452 ($\pm$1.093) & \cellcolor[rgb]{ .98,  .51,  .439}11.5731 ($\pm$1.193)   & \cellcolor[rgb]{ .996,  .816,  .498}7.872 ($\pm$0.92)    & \cellcolor[rgb]{ .988,  .659,  .471}9.7527 ($\pm$1.083)  & \cellcolor[rgb]{ .98,  .557,  .451}10.9785 ($\pm$1.108)  & \cellcolor[rgb]{ .973,  .412,  .42}12.7097 ($\pm$1.478)  \\
			\textbf{parkinsons}           & \cellcolor[rgb]{ .412,  .749,  .482}2.4677 ($\pm$1.497)                   & \cellcolor[rgb]{ .388,  .745,  .482}2.2333 ($\pm$1.742) & \cellcolor[rgb]{ .541,  .788,  .49}3.5656 ($\pm$2.492)  & \cellcolor[rgb]{ .655,  .82,  .494}4.572 ($\pm$1.934)   & \cellcolor[rgb]{ 1,  .922,  .518}7.5355 ($\pm$1.44)     & \cellcolor[rgb]{ .635,  .816,  .494}4.3839 ($\pm$1.861) & \cellcolor[rgb]{ .875,  .882,  .51}6.472 ($\pm$2.423)   & \cellcolor[rgb]{ .996,  .843,  .506}8.3161 ($\pm$1.644) & \cellcolor[rgb]{ 1,  .898,  .514}7.7968 ($\pm$1.719)     & \cellcolor[rgb]{ .996,  .827,  .502}8.4892 ($\pm$1.901)  & \cellcolor[rgb]{ .98,  .494,  .435}11.7516 ($\pm$1.155)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5419 ($\pm$1.351)  & \cellcolor[rgb]{ .984,  .584,  .455}10.8742 ($\pm$1.317) \\
			\textbf{student\_performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.5634 ($\pm$1.912)                   & \cellcolor[rgb]{ .98,  .506,  .439}11.3978 ($\pm$2.178) & \cellcolor[rgb]{ .973,  .412,  .42}12.4312 ($\pm$1.34)  & \cellcolor[rgb]{ .843,  .875,  .506}5.6624 ($\pm$3.57)  & \cellcolor[rgb]{ .478,  .769,  .486}3.1935 ($\pm$2.12)  & \cellcolor[rgb]{ .875,  .882,  .51}5.8634 ($\pm$3.159)  & \cellcolor[rgb]{ .514,  .78,  .486}3.4194 ($\pm$2.006)  & \cellcolor[rgb]{ 1,  .902,  .514}6.9333 ($\pm$2.44)     & \cellcolor[rgb]{ 1,  .886,  .514}7.1032 ($\pm$1.989)     & \cellcolor[rgb]{ .98,  .537,  .443}11.0624 ($\pm$1.067)  & \cellcolor[rgb]{ .988,  .918,  .514}6.6366 ($\pm$2.023)  & \cellcolor[rgb]{ 1,  .922,  .518}6.7011 ($\pm$2.242)     & \cellcolor[rgb]{ .996,  .804,  .498}8.0323 ($\pm$1.935)  \\
			\textbf{wine\_quality}        & \cellcolor[rgb]{ .569,  .796,  .49}3.2806 ($\pm$1.931)                    & \cellcolor[rgb]{ .388,  .745,  .482}2.1118 ($\pm$1.666) & \cellcolor[rgb]{ .624,  .812,  .494}3.6301 ($\pm$1.731) & \cellcolor[rgb]{ .808,  .863,  .506}4.7882 ($\pm$2.105) & \cellcolor[rgb]{ .706,  .835,  .498}4.1505 ($\pm$1.916) & \cellcolor[rgb]{ .871,  .882,  .51}5.1925 ($\pm$1.951)  & \cellcolor[rgb]{ 1,  .922,  .518}6.0011 ($\pm$2.404)    & \cellcolor[rgb]{ .988,  .647,  .467}9.5935 ($\pm$1.494) & \cellcolor[rgb]{ .984,  .588,  .455}10.3387 ($\pm$1.62)  & \cellcolor[rgb]{ .98,  .525,  .443}11.1602 ($\pm$1.773)  & \cellcolor[rgb]{ .992,  .722,  .482}8.6344 ($\pm$1.18)   & \cellcolor[rgb]{ .988,  .651,  .467}9.5269 ($\pm$1.341)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5903 ($\pm$1.352)  \\
			\textbf{avg rank}             & \cellcolor[rgb]{ .388,  .745,  .482}3.5512 ($\pm$2.25)                    & \cellcolor[rgb]{ .471,  .769,  .486}3.9314 ($\pm$3.423) & \cellcolor[rgb]{ .616,  .808,  .494}4.5691 ($\pm$3.517) & \cellcolor[rgb]{ .631,  .812,  .494}4.6346 ($\pm$2.364) & \cellcolor[rgb]{ .675,  .827,  .498}4.8394 ($\pm$2.384) & \cellcolor[rgb]{ .808,  .867,  .506}5.4327 ($\pm$2.9)   & \cellcolor[rgb]{ 1,  .922,  .518}6.2727 ($\pm$3.004)    & \cellcolor[rgb]{ .992,  .776,  .49}7.7855 ($\pm$2.271)  & \cellcolor[rgb]{ .988,  .639,  .467}9.1522 ($\pm$2.48)   & \cellcolor[rgb]{ .984,  .612,  .459}9.4451 ($\pm$2.75)   & \cellcolor[rgb]{ .984,  .592,  .455}9.6445 ($\pm$2.214)  & \cellcolor[rgb]{ .98,  .529,  .443}10.2877 ($\pm$2.346)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4538 ($\pm$2.354)  \\
			\textbf{normalised avg rank}  & \cellcolor[rgb]{ .388,  .745,  .482}1                                     & \cellcolor[rgb]{ .49,  .773,  .486}2                    & \cellcolor[rgb]{ .592,  .804,  .494}3                   & \cellcolor[rgb]{ .694,  .831,  .498}4                   & \cellcolor[rgb]{ .796,  .863,  .506}5                   & \cellcolor[rgb]{ .898,  .89,  .51}6                     & \cellcolor[rgb]{ 1,  .922,  .518}7                      & \cellcolor[rgb]{ .996,  .839,  .502}8                   & \cellcolor[rgb]{ .992,  .753,  .486}9                    & \cellcolor[rgb]{ .988,  .667,  .471}10                   & \cellcolor[rgb]{ .984,  .584,  .455}11                   & \cellcolor[rgb]{ .98,  .498,  .439}12                    & \cellcolor[rgb]{ .973,  .412,  .42}13                    \\
			\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\end{tabular}%

	}
\end{sidewaystable}%

\begin{sidewaystable}[htbp]

@@

		% Table generated by Excel2LaTeX from sheet 'loss'
		\begin{tabular}{r|lll|l|l|l|l|l|lllll}
			                                    & \multicolumn{13}{c}{\textbf{BHH vs. Low-Level Heuristics - Average Loss}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         \\
			\cmidrule{2-14}    \textbf{dataset} & \multicolumn{1}{c}{\textbf{adagrad}}                                      & \multicolumn{1}{c}{\textbf{adam}}                       & \multicolumn{1}{c|}{\textbf{rmsprop}}                   & \multicolumn{1}{c|}{\textbf{bhh\_gd}}                   & \multicolumn{1}{c|}{\textbf{nag}}                       & \multicolumn{1}{c|}{\textbf{bhh\_all}}                  & \multicolumn{1}{c|}{\textbf{adadelta}}                  & \multicolumn{1}{c|}{\textbf{bhh\_mh}}                   & \multicolumn{1}{c}{\textbf{ga}}                         & \multicolumn{1}{c}{\textbf{pso}}                        & \multicolumn{1}{c}{\textbf{sgd}}                        & \multicolumn{1}{c}{\textbf{momentum}}                   & \multicolumn{1}{c}{\textbf{de}}                         \\

@@

			\textbf{abalone}                    & \cellcolor[rgb]{ .506,  .776,  .486}1.9678 ($\pm$0.032)                   & \cellcolor[rgb]{ .494,  .773,  .486}1.9651 ($\pm$0.035) & \cellcolor[rgb]{ .388,  .745,  .482}1.9455 ($\pm$0.035) & \cellcolor[rgb]{ .749,  .847,  .502}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .765,  .851,  .502}2.0156 ($\pm$0.035) & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)    & \cellcolor[rgb]{ .788,  .859,  .502}2.0199 ($\pm$0.034) & \cellcolor[rgb]{ .996,  .827,  .502}2.2942 ($\pm$0.055) & \cellcolor[rgb]{ .984,  .612,  .459}2.8155 ($\pm$0.055) & \cellcolor[rgb]{ .98,  .522,  .443}3.0384 ($\pm$0.294)  & \cellcolor[rgb]{ .992,  .773,  .49}2.428 ($\pm$0.029)   & \cellcolor[rgb]{ .992,  .745,  .486}2.4942 ($\pm$0.029) & \cellcolor[rgb]{ .973,  .412,  .42}3.2959 ($\pm$0.016)  \\
			\textbf{air\_quality}               & \cellcolor[rgb]{ .651,  .82,  .494}0.2569 ($\pm$0.007)                    & \cellcolor[rgb]{ .827,  .871,  .506}0.2606 ($\pm$0.009) & \cellcolor[rgb]{ .388,  .745,  .482}0.2513 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .996,  .827,  .502}0.2729 ($\pm$0.016) & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .976,  .914,  .514}0.2637 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .792,  .494}0.2759 ($\pm$0.008) & \cellcolor[rgb]{ .984,  .608,  .459}0.2923 ($\pm$0.023) & \cellcolor[rgb]{ .988,  .69,  .475}0.2852 ($\pm$0.015)  & \cellcolor[rgb]{ .984,  .604,  .459}0.2929 ($\pm$0.016) & \cellcolor[rgb]{ .973,  .412,  .42}0.3097 ($\pm$0.017)  \\
			\textbf{bank}                       & \cellcolor[rgb]{ .459,  .765,  .486}0.2096 ($\pm$0.005)                   & \cellcolor[rgb]{ .4,  .745,  .482}0.2065 ($\pm$0.004)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2058 ($\pm$0.006) & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.005)    & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .886,  .514}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .627,  .812,  .494}0.2186 ($\pm$0.004) & \cellcolor[rgb]{ .996,  .839,  .502}0.2562 ($\pm$0.011) & \cellcolor[rgb]{ .988,  .686,  .475}0.2881 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.3454 ($\pm$0.034)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2382 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .922,  .518}0.2386 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .424,  .424}0.3437 ($\pm$0.028) \\
			\textbf{bike}                       & \cellcolor[rgb]{ .388,  .745,  .482}0.0458 ($\pm$0.002)                   & \cellcolor[rgb]{ .592,  .804,  .494}0.0682 ($\pm$0.068) & \cellcolor[rgb]{ 1,  .922,  .518}0.1123 ($\pm$0.103)    & \cellcolor[rgb]{ .467,  .765,  .486}0.0545 ($\pm$0.005) & \cellcolor[rgb]{ .882,  .886,  .51}0.0995 ($\pm$0.002)  & \cellcolor[rgb]{ .565,  .796,  .49}0.0651 ($\pm$0.02)   & \cellcolor[rgb]{ .588,  .8,  .49}0.0679 ($\pm$0.002)    & \cellcolor[rgb]{ 1,  .902,  .514}0.1179 ($\pm$0.006)    & \cellcolor[rgb]{ .992,  .761,  .486}0.1531 ($\pm$0.005) & \cellcolor[rgb]{ .992,  .773,  .49}0.1503 ($\pm$0.025)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1599 ($\pm$0.003) & \cellcolor[rgb]{ .992,  .725,  .482}0.1614 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.2399 ($\pm$0.04)   \\
